Tensor anisotropy as a tracer of cosmic voids

### 2015-05-26 RefereeResponse.md

7. **I'm confused a bit about the middle panels of Fig. 1. The title,
    "Visual impresion for lambda_th=..."  is strange. Aren't there
    several thresholds here? Also, what are the blue dots? Also
    "impresion" is  misspelled.**

    Response:
    - We have rewritten the caption. There are two different
    thresholds, one for each web finder. Blue dots were dark matter
    halos (FOF). We removed them for clarity. The typo ("impresion")
    is  also corrected.

8. **Sect 3.3, 2nd paragraph: I do not see why "the analysis of [y]our
    results" shows that a fixed Cartesian  mesh does not induce
    spurious results". It's true, that the results look reasonable,
    but I think it would  be better to state something about the level
    of discreteness noise, e.g. the number of zero-density cells,  or
    the minimum if there are none.**

    Response:
    We have rephrased this in terms of the number of particles per
    cell in the lowest density regions.

@@

9. **Sect. 5.4: The sentence "subcompensated voids have outflowing ve-
    locity profiles all the way up to the effective radius where the
    average radial density reaches the average value" is a bit
    confusing; this is not r_eff, right? If so, this statement seems
    to be an understatement (v_r >0 out to several r_eff,
    typically). If not, "effective" should be removed for clarity.**

    Response:
    We removed "effective" for clarity.

10. **In Sect. 5.5, there are a few instances where I think you meant "r/r_eff =" instead of "r_eff =".**

    Response:
    We have revised all the instances and replaced r_eff by r/r_eff
    wherever it was appropriate.

@@

11. **All quantities are computed at the pixel scale, ~1 Mpc/h,
    correct? If the authors have any insights about  how the results
    would change if this scale were changed, it would be helpful to
    state them. A quantitative  discussion of how some results would
    change with a different scale would be great, but not necessary.**

    Response:
    We now mention in the first paragraph of the Results section the
    expected results for larger smoothing scales. Namely, that the
    statistics for the cosmci web tend to be those of a random
    Gaussian field.

### 2015-05-26 cosmic_voids.tex
solved minor issue #21 sobre lo que pasaria con otra smoothing scale

We limit our results to voids with effective radius larger than the
smoothing length of the density field, i.e. $\sim 1$\hMpc.  
Below that scale numerical resolution effects become important. 
With that choice we find a void volume filling fraction $54.88\%$ and
$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.

>>>>

We limit our results to voids with effective radius larger than the
smoothing length of the density field, i.e. $\sim 1$\hMpc.  
\before{Below that scale numerical resolution effects become
  important. }
\after{For smaller interpolation/smoothing scales the shot noise in
  the low density regions starts to be noticeable.}
With that choice we find a void volume filling fraction $54.88\%$ and
$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.  
\after{For larger smoothing scales ($>5\hMpc$) the density and shear fields
  tend to be Gaussian and therefore follow closely the analytical environment abundance
  predictions for Gaussian random fields \citep{Forero09,Alonso2015}. }
